
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Daniel Buscombe
% @author   Daniel Buscombe
% @date     June 2013

%________________________________________________________________________________________
\documentclass[margin,line]{resume}

\usepackage{url}

\begin{document}
\name{\Large Daniel Buscombe}
\begin{resume}

Research Geologist, United States Geological Survey,\\
Grand Canyon Monitoring and Research Center, 2255 N Gemini Drive, Flagstaff, AZ 86001 \\
http://dbuscombe-usgs.github.com

%    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{2mm}

    \begin{tabular}{@{} l @{\hspace{20mm}} r}
    Tel: 928-556-7216 & email: dbuscombe@usgs.gov \\
    \end{tabular}

    %____________________________________________________________________________________
%    % Research Interests
%\section{\mysidestyle Research\\Interests}
%     I am a geomorphologist/sedimentologist with a principal research interest in sediment dynamics, which includes the physical and biochemical makeup of sediment beds in a range of aquatic environments, the role of sediment heterogeneity in the physics of sediment transport, and the morphodynamics (both micro- and macro-scale) that result from sediment transport, sedimentation, stratigraphy and geomorphological forms. I study the complex inter-relations between fluid flows, geomorphology, sediment transport and sedimentology. I investigate these processes by developing novel field-deployed optical and acoustic imaging systems, and computational algorithms for small-scale sediment hydroacoustics, in-situ particle and bed imaging and flow-field/turbulence measurements. 


    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

        \begin{footnotesize}
    {\bf Ph.D. (2008), Coastal Geomorphology/Nearshore Oceanography, University of Plymouth}, Plymouth, UK. {\sl Morphodynamics, Sediment Dynamics and Sedimentation of a Gravel Beach}. Advisor:  Prof. Gerhard Masselink.

    {\bf BSc (Hons), 1st class (2003), Physical Geography with Minors in Environmental Sciences and Biology, Lancaster University}, Lancaster, UK.  {\sl Morphodynamics of a Ridge-and-Runnel System on a Macrotidal Beach}. Advisor:  Dr Suzanna Ilic. 
        \end{footnotesize}

    %____________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Employment\\History}

        \begin{footnotesize}
        \begin{list1}
    \item[1]{\bf November 2012 --  present}. {\sl Research Geologist, Grand Canyon Monitoring and Research Center, U.S. Geological Survey, Flagstaff, AZ, USA.}
    \item[2]{\bf October 2009 -- November 2012}. {\sl Post-doctoral Research Fellow, School of Marine Science \& Engineering, University of Plymouth, UK.} 
    \item[3]{\bf September, 2008 -- 2011}. {\sl Computer Programming Contractor, Marine Biology \& Ecology Research Centre, University of Plymouth, UK.} 
    \item[4]{\bf October, 2008 -- October 2009}. {\sl Post-doctoral Research Scholar, United States Geological Survey, Santa Cruz, California, USA.} 
    \item[5]{\bf June, 2008 -- September, 2008}. {\sl Research Assistant, School of Geography, University of Plymouth, UK.} 
    \item[6]{\bf December, 2007 -- April, 2008}. {\sl Research Assistant, School of Earth, Ocean \& Environmental Science, University of Plymouth, UK.} 
   \item[7] {\bf October, 2004 -- July 2008}. {\sl Associate Lecturer and Demonstrator (part-time), School of Geography, University of Plymouth, UK.}
    \item[8]{\bf August 2003 - September, 2004}. {\sl Assistant tutor, Field Studies Council, Castle Head, Grange-over-Sands, UK}.
    \end{list1}
        \end{footnotesize}

    %____________________________________________________________________________________
    % Publications
    \section{\mysidestyle Ten Selected Publications}

        \begin{footnotesize}
	\begin{list1}
	\item[1] {\bf Buscombe, D.}, and Masselink, G. (2006) Concepts in Gravel Beach Dynamics. {\sl EARTH SCIENCE REVIEWS} 79, 33-52.\\
	
	%\item[2] Masselink, G., {\bf Buscombe, D.}, Austin, M.J, O'Hare, T., Russell, P. (2008) Sediment Trend Models Fail to Reproduce Small Scale Sediment Transport Patterns on an Intertidal Beach. {\sl Sedimentology} 55, 667-687.\\
	
	\item[2] Austin, M.J., and {\bf Buscombe, D.} (2008) Morphological Change and Sediment Dynamics of the Beach Step on a Macrotidal Gravel Beach. {\sl MARINE GEOLOGY} 249, 167-183. \\

	\item[3] {\bf Buscombe, D.}, Rubin, D.M., and Warrick, J.A. (2010) Universal Approximation of Grain Size from Images of Non-Cohesive Sediment. {\sl JOURNAL OF GEOPHYSICAL RESEARCH - EARTH SURFACE} 115, F02015.\\

	\item[4] Williams, J.J., {\bf Buscombe, D.}, Masselink, G., Turner, I., and Swinkels, C. (2012) Barrier Dynamics Experiment (BARDEX): Aims, Design and Procedures. {\sl COASTAL ENGINEERING} 63, 3-12.\\

	\item[5] {\bf Buscombe, D.}, and Conley, D.C. (2012) Effective Shear Stress of Graded Sediment. {\sl WATER RESOURCES RESEARCH} 48, W05506.\\

	\item[6] {\bf Buscombe, D.}, and Rubin, D.M. (2012) Advances in the Simulation and Automated Measurement of Granular Material, Part 1: Simulations. {\sl JOURNAL OF GEOPHYSICAL RESEARCH - EARTH SURFACE} 117, F02001.\\

	\item[7] Lacy, J.R., Rubin, D.M. and {\bf Buscombe, D.} (2012) Currents and sediment transport induced by a tsunami far from its source. {\sl JOURNAL OF GEOPHYSICAL RESEARCH - OCEANS} 117, C09028.\\

    \item[8] {\bf Buscombe, D.} (2013) Transferable Wavelet Method for Grain Size-Distribution from Images of Sediment Surfaces and Thin Sections, and Other Natural Granular Patterns. {\sl SEDIMENTOLOGY} 60, 1709--1732.\\

%	\item[9] {\bf Buscombe, D.}, Rubin, D.M., Lacy, J.R., Storlazzi, C., Hatcher, G., Chezar, H., Wyland, R. and Sherwood, C. (2014) Autonomous bed-sediment imaging-systems for revealing temporal variability of grain size. {\sl Limnology and Oceanography: Methods, 12, 390 - 406}\\

	\item[9] {\bf Buscombe, D.}, Grams, P.E., Kaplinski, M.A. (2014), Characterizing riverbed sediment using high-frequency acoustics 2: Scattering signatures of Colorado River bed sediment in Marble and Grand Canyons. {\sl JOURNAL OF GEOPHYSICAL RESEARCH - EARTH SURFACE}, 119, doi:10.1002/2014JF003191.\\

	\item[10] {\bf Buscombe, D.}, Grams, P.E., Smith, S.M., 2015, Automated riverbed sediment classification using low-cost sidescan sonar. {\sl JOURNAL OF HYDRAULIC ENGINEERING}, 10.1061/(ASCE)HY.1943-7900.0001079, 06015019.\\

	\end{list1}
        \end{footnotesize}
        

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF
